\documentclass{andres_cv}

\setname{Andres }{Jalife}
\setaddress{Bs.As / Argentina}
\setmobile{1136832584}
\setmail{andyjalife@gmail.com}
\setposition{Work Student}


\setlinkedinaccount{https://www.linkedin.com/in/andres-j-91169811a/} 
\setgithubaccount{https://github.com/AndresJalife} 
\setthemecolor{red} 

\begin{document}
\headerview
\vspace{1ex}

%Sections

% Summary
\addblocktext{Summary}{
Computer science student in Universidad de Buenos Aires, Argentina and Full Stack developer at Odea SRL. Im 22 years old and passionate about what I do. I always willing to learn new technologies and improve the ones I already know. I can communicate fluently in Spanish and English. 
}

%Education
\section{Education} 
    \datedexperience{Buenos Aires University}{2018-2023 [expected]} 
    \explanation{B.D in Computer Engineering} 
     \explanationdetail{\coloredbullet\ % 
     Currently pursuing my third year with two more to go
     }
    \datedexperience{ORT}{2012-2017}
    \explanation{High School}
        \explanationdetail{\coloredbullet\ % 
        Graduated with honors. Average: 8.3}

% Experience
\section{Experience}
    \datedexperience{ODEA SRL}{NOV 2020-NOW / BSAS} 
    \explanation{Full Stack Developer} 
    \explanationdetail{\coloredbullet\ Front-End developtment on HTML, CSS, JS.}
    \explanationdetail{\coloredbullet\ Back-End development on Flink and Spring Boot [JAVA]}
    \explanationdetail{\coloredbullet\ Mobile Development in React Native}
    
    \explanationdetail{ I started as a Front-End developer and after some time, given that I knew Java, they offered me to learn, by my own means, Flink, a very interesting Apache Framework. Since then I've been developing a real-time software to analyze data (besides the Front-End development). They've also asked if I wanted to learn Spring Boot to develop websockets with Java, which I'm happily doing at the moment.}
    
\section{Projects}
    \datedexperience{ChowProject}{JAVA - LIBGDX} 
    \explanationdetail{1v1 fight game. Developed with ChowJuanCo (Animation Studio) as the graphics directors.} 
    \explanationdetail{Currently stopped due to lack of time} 

% Skills
\section{Skills}
    
    \newcommand{\skillone}{\createskill{Programming Languages}{Java \cpshalf Javascript \cpshalf HTML \cpshalf CSS \cpshalf Python \cpshalf SmallTalk \cpshalf Java \cpshalf Rust \cpshalf SQL}}
    
    \newcommand{\skilltwo}{\createskill{Software Development}{Programming Paradigms \cpshalf GIT \cpshalf CLI \cpshalf Agile Methodology \cpshalf MVC \cpshalf TDD \cpshalf BDD}}
    
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{React \cpshalf React Native \cpshalf Flink \cpshalf Pandas  \cpshalf Spring Boot \cpshalf WebPack \cpshalf Jupyter}}
    
    \newcommand{\skillfour}{\createskill{Databases}{PostgreSQL \cpshalf Redis}}
    
    \newcommand{\skillfive}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Spanish \ \ \textbf{\emph{Fluent:}} \ \ English }}
    
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive}

\section{Certificates}
    \newcommand{\extraone}{
    First Certificate In English (FCE Cambridge) [ID : 17BAR6025402]
    }
    
    \newcommand{\extratwo}{
    Finance for non financial professionals [Coursera | ID : PHPBPT3EC6L8]
    }
    
    \newcommand{\listofextras}{\extraone, \extratwo}
    
    \createbullets{\listofextras}

\createfootnote
\end{document}

